Project Light

### 2015-09-09 paper/paper.tex
formulate rest of related work section

The problem of wireless and user-friendly key predistribution / key provisioning remains.
There are multiple approaches to solve this:

@@

- some ideas to transmit keys via light:

- Blink 'Em All \cite{saxena2009blink} lets motes LEDs blink and computer with connected camera read it.

- LiDSN \cite{doan2012lidsn} same with special connector-hardware where mote gets put into. if mote has no led, light sensor is assumed and connector emits light. Proved as usable by end-user, but special hardware needed

- Electric Imp \cite{electricimp} sells proprietary BlinkUp technology: uses smart phone for flickering -> good for end users
- not scientifically examined till now (as far as we know)

thus, we propose a user-friendly wireless key provisioning protocols without additional hardware needed, just mote with light sensor and smart phone.

>>>>

The problem of wireless and user-friendly key predistribution / key provisioning remains.
There are multiple approaches to solve this by securing the radio channel in some way, e.g.:

@@

There are also some proposals for key predistribution using an alternative channel, i.g. light.

\cite{saxena2009blink} proposes to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
They are then verified using the unidirectional light channel from the motes to the sink.

\textit{Light Communication for Deploying Secure Wireless Sensor Networks (LiDSN)} is an approach to assign a node id and a secret key to a mote, \cite{doan2012lidsn}.
Therefore, a temporal key for radio communication is transmitted to a specialized \textit{connector} via light.
The communication via light can be either way: if the connector receives light from the motes LED, it reads it. If the mote has no LED, a light sensor is assumed and the connector emits light with an own led.
It is shown, that key provisioning is both faster and easier for end users.

\cite{electricimp} sells proprietary BlinkUp~\texttrademark  technology.
Instead of specialized hardware which end users might not want to buy, they provide a smart phone application which provisions a mote.
Assuming most users who install IoT setups already own a smart phone, this seems to be a cost-effective alternative.

However, we could not find that this approach is examined scientifically.
Thus, we propose an protocol for secure and wireless key predistribution using a smart phone as light emitter and motes with a light sensor as receivers.
